\bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}

### 2018-02-27 latex/paper.tex
Additional edits

\documentclass[12pt, twoside, letterpaper]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage[parfill]{parskip}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{charter}
\usepackage[numbers]{natbib}
\usepackage[draft]{graphicx}  %% remove [draft] to compile with pictures
\graphicspath{{../figures/}}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

@@

\section{Discussion}
Cilia are essential for proper human development, and their disruption
can cause genetic disorders with severities ranging from congenital-
lethal \citep{}
to late onset \citep{}.
A large number of ciliopathies are associated with genes that encode for
proteins that function at the cilium transition zone (TZ).
Often, a single gene is linked to multiple ciliopathies with
a spectrum of phenotypes and severities.
For example, \textit{CEP290} is linked to at least six different
cilium-associated human disorders.
It is likely that these mutations do not completely abolish CEP290
function, and may be affected by genetic modifiers in an affected individual
\citep{zaghloul2010functional, khanna2009common, leitch2008hypomorphic}.
Animal models with partial loss of TZ function may therefore provide
insight on intermediate phenotypes associated with human disease.
Here, we found that reduced levels of the membrane lipid \PIP{},
which is known to be enriched at the base of cilia,
affects TZ maturation, but not assembly,
leading to hyperelongated TZs that show signs of functional defects, and
may represent one such modifier for TZ function.

@@

%%
%    FIGURE 2
%
\textbf{Figure 2. Sktl is important for transition zone maturation and localizes to basal bodies.}
\begin{enumerate}[label={(\Alph*)}, nolistsep]
\item Expression of full-length Sktl suppresses \sigd{}-induced TZ hyperelongation.
\item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and Sktl; \sigd{} ($n$\textgreater 60) from (A).
\item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation. Cilia are marked using
  Unc-GFP.
\item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
  The scale bar represents expected amino acid substitutions per site and branch support values are shown in red (a value of 1 indicates maximum support).
Abbreviations: Cele (\textit{Caenorhabditis elegans}), Spur (\textit{Strongylocentrotus purpuratus}), Amel (\textit{Apis mellifera}), Aaeg (\textit{Aedes aegypti}), Dana (\textit{Drosophila ananassae}), Dmel (\textit{Drosophila melanogaster}), Hsap (\textit{Homo sapiens}), Mmus (\textit{Mus musculus}), Xtro (\textit{Xenopus tropicalis}), Cint (\textit{Ciona intestinalis}), Scer (\textit{Saccharomyces cerevisiae}).
\end{enumerate}

\begin{figure}[ht]
  \includegraphics[scale=0.9]{figure-2/figure2.png}
\end{figure}
\newpage

%%
%    FIGURE 3
%
\textbf{Figure 3. Hyperelongated transition zones display functional defects.}
\begin{enumerate}[label={(\Alph*)}, nolistsep]
\item
\item
\item
\item
\end{enumerate}

\begin{figure}[ht]
  \includegraphics[scale=0.8]{figure-3/figure3.png}
\end{figure}
\newpage

%%%
%%    FIGURE 4
%%
\textbf{Figure 4. The \textit{onion rings} (\textit{onr}) allele of \textit{d}Exo84 decouples TZ hyperlongation from loss of plasma membrane contacts.}
\begin{enumerate}[label={(\Alph*)}, nolistsep]
\item Cells mutant for \textit{onr} do not display hyperelongated TZs marked with acetylated tubulin.
\item Quantification from (A).
\item Cells mutant for \textit{onr} display loss of plasma membrane tethering.
\end{enumerate}

\begin{figure}[ht]
  \includegraphics[scale=0.9]{figure-4/figure4.png}
\end{figure}
\newpage

\end{document}

>>>>

\documentclass[12pt, twoside, letterpaper]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage[parfill]{parskip}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{charter}
\usepackage[numbers]{natbib}
\usepackage{graphicx}
\graphicspath{{../figures/}}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

@@

\section{Discussion}
Cilia are tiny organelles that are essential for proper human development
and cilium-associated developmental disorders are known as ciliopathies.
A large number of ciliopathies are linked to genes that encode
transition zone (TZ) proteins.
Often, a single gene is linked to multiple ciliopathies with
a spectrum of phenotypes and severities.
For example, \textit{CEP290} is linked to at least six different
cilium-associated human disorders.
It is likely that these mutations do not completely abolish CEP290
function, and may be affected by genetic modifiers in an affected individual
\citep{zaghloul2010functional, khanna2009common, leitch2008hypomorphic}.
Animal models with partial loss of TZ function may therefore provide
insight on intermediate phenotypes associated with human disease.
Here, we found that reduced levels of the membrane lipid \PIP{},
which is known to be enriched at the base of cilia,
affects TZ maturation, but not assembly,
leading to hyperelongated TZs that show signs of functional defects, and
may represent one such modifier for TZ function.

@@

%%
%%%%
%%%    FIGURE 2
%%%
%%\textbf{Figure 2. Sktl is important for transition zone maturation and localizes to basal bodies.}
%%\begin{enumerate}[label={(\Alph*)}, nolistsep]
%%\item Expression of full-length Sktl suppresses \sigd{}-induced TZ hyperelongation.
%%\item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and Sktl; \sigd{} ($n$\textgreater 60) from (A).
%%\item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation. Cilia are marked using
%%  Unc-GFP.
%%\item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
%%  The scale bar represents expected amino acid substitutions per site and branch support values are shown in red (a value of 1 indicates maximum support).
%%Abbreviations: Cele (\textit{Caenorhabditis elegans}), Spur (\textit{Strongylocentrotus purpuratus}), Amel (\textit{Apis mellifera}), Aaeg (\textit{Aedes aegypti}), Dana (\textit{Drosophila ananassae}), Dmel (\textit{Drosophila melanogaster}), Hsap (\textit{Homo sapiens}), Mmus (\textit{Mus musculus}), Xtro (\textit{Xenopus tropicalis}), Cint (\textit{Ciona intestinalis}), Scer (\textit{Saccharomyces cerevisiae}).
%%\end{enumerate}
%%
%%\begin{figure}[ht]
%%  \includegraphics[scale=0.9]{figure-2/figure2.png}
%%\end{figure}
%%\newpage
%%
%%
%%%%
%%%    FIGURE 3
%%%
%%\textbf{Figure 3. Hyperelongated transition zones display functional defects.}
%%\begin{enumerate}[label={(\Alph*)}, nolistsep]
%%\item
%%\item
%%\item
%%\item
%%\end{enumerate}
%%
%%\begin{figure}[ht]
%%  \includegraphics[scale=0.8]{figure-3/figure3.png}
%%\end{figure}
%%\newpage
%%
%%
%%%%%
%%%%    FIGURE 4
%%%%
%%\textbf{Figure 4. The \textit{onion rings} (\textit{onr}) allele of \textit{d}Exo84 decouples TZ hyperlongation from loss of plasma membrane contacts.}
%%\begin{enumerate}[label={(\Alph*)}, nolistsep]
%%\item Cells mutant for \textit{onr} do not display hyperelongated TZs marked with acetylated tubulin.
%%\item Quantification from (A).
%%\item Cells mutant for \textit{onr} display loss of plasma membrane tethering.
%%\end{enumerate}
%%
%%\begin{figure}[ht]
%%  \includegraphics[scale=0.9]{figure-4/figure4.png}
%%\end{figure}
%%\newpage
%%
%%
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
